Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-12-12 paper/paper.tex
Last paper changes and first presentation commit
add conference submission line

\title{SAFETY ANALYSIS OF THE MOLTEN SALT FAST REACTOR FUEL COMPOSITION USING
MOLTRES \\~\\~\\~\\}
\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
Kathryn D. Huff$^a$}
\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering,
University of Illinois at Urbana-Champaign}
\email{$^b$smpark3@illinois.edu}

@@

%\begin{center}
%\section*{Acknowledgements}
%\end{center}

%Acknowledgements \\

>>>>

\title{SAFETY ANALYSIS OF THE MOLTEN SALT FAST REACTOR FUEL COMPOSITION USING
MOLTRES \\ \textit{(Preprint submitted to ANS Global 2019 International Fuel
Cycle Conference)} \\~\\~\\}
\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
Kathryn D. Huff$^a$}
\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering,
University of Illinois at Urbana-Champaign}
\email{$^b$smpark3@illinois.edu}

@@

\begin{center}
\section*{Acknowledgements}
\end{center}
The authors thank members of the \gls{ARFC} group at the University of Illinois
at Urbana-Champaign for helpful discussions relating to this paper. Sun Myung
Park is supported by the Singapore Nuclear Research and Safety Initiative
(SNRSI) Postgraduate Scholarship.
